\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{listings}
\lstset{basicstyle=\ttfamily}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{hyperref}

\title{CS 3468 -- Homework 4}
\author{Stuart Olsen}

\begin{document}
\maketitle

\section*{Chapter 4}
\subsection*{What is an ISA?}

\subsection*{What features does an ISA define?}

\subsection*{Name and describe the three most common ISA models on which architectures are based.}

\subsection*{Name and describe two types of ISAs that fall under each of the three ISA models.}

\subsection*{According to the von Neumann model, list and define the major components of the CPU.}

\subsection*{Draw and describe the memory hierarchy of an embedded system.}

\subsection*{Name and describe the two most common type of units that manage memory.}

\section*{Additional Questions}
\subsection*{Draw the layout of the data memory space in the ATmega128 (i.e., general registers, I/O registers, and data).}

\subsection*{Find the memory address and the I/O address (if available) for the following special registers:}
\begin{itemize}
\item I/O registers for port A: {\ttfamily PORTA}, {\ttfamily DDRA}, {\ttfamily PINA}
\item Stack pointer registers: {\ttfamily SPH}, {\ttfamily SPL}
\item Status register: {\ttfamily SREG}
\item MCU control register: {\ttfamily MCUCR}
\item Interrupt control and status registers: {\ttfamily EIMSK}, {\ttfamily EIFR}
\item USART0 registers: {\ttfamily UDR0}, {\ttfamily UCSR0A}, {\ttfamily UCSR0B}, {\ttfamily UCSR0C}, {\ttfamily UBRR0H}, {\ttfamily UBRR0L}
\end{itemize}

\subsection*{Dynamic Voltage Scaling (DVS) is a technique to control energy consumption of a processor. It is based on the two equations below, where $V$ is the voltage supplied to the processor, $P$ is the power consumption, and $f$ is the scaled processor frequency. Assume $C = \SI{2.75}{\watt\per\volt^2}$, $F = \SI{3.8}{\giga\hertz}$, and $K = \SI{1.563}{\volt}$.}

\begin{align}
  P &= C \cdot V^2\\
  f &= F \cdot (1 - \frac{K}{V})
\end{align}

\subsubsection*{If $V = \SI{3}{\volt}$, what are $P$ and $f$? What is the total energy consumed by the task?}

\subsubsection*{If $V = \SI{2}{\volt}$, what are $P$ and $f$? What is the total energy consumed by the task?}

\end{document}
