\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{listings}
\lstset{basicstyle=\ttfamily}
\usepackage{graphicx}
\usepackage{siunitx}
\DeclareSIUnit{\degreeFahrenheit}{\degree F}
\usepackage{amsmath}
\usepackage{hyperref}

\newcommand{\SIfrac}[3]{
  {\ensuremath{\frac{\num{#1}}{\num{#2}}\,\si{#3}}}
}

\title{CS 3468 -- Homework 2}
\author{Stuart Olsen}

\begin{document}
\maketitle

\section*{Chapter 3}
\subsection*{Given the simple flashlight shown in Figure 3-38, draw a corresponding schematic diagram. Please use the schematic symbols on page 594.}

\subsection*{What is an LED?}
An LED, or a light-emitting diode, is a semiconductor device which emits light when a current is applied across its leads. Electrically, it functions as a diode.

\subsection*{How does an LED work?}

\subsection*{What is an IC?}

\subsection*{Name and describe the classes of ICs according to the number of electronic components they contain.}

\subsection*{Identify at least five ICs in Figures 3-37a and b under problem 1 of this section. Describe what these ICs are.}

\section*{Additional Questions}
\renewcommand{\thesubsubsection}{\alph{subsubsection}}

\subsection*{The resistance of a thermistor changes according to the temperature. In the right circuit, the resistance function of the thermistor is $R_0 = \SI{10000}{\ohm} + \SI{60}{\ohm\per\degreeFahrenheit} \cdot T$. The other resistor is $R_1 = \SI{10000}{\ohm}$. The output voltage on $R_1$ is $V_0 = \SI{3}{\volt} \cdot \frac{R_1}{R_0 + R_1}$.}
\setcounter{subsubsection}{0}
\subsubsection{If the room temperature is $T = \SI{70}{\degreeFahrenheit}$, what is $V_0$?}
\begin{align*}
  V_0 &= \SI{3}{\volt} \cdot \frac{R_1}{R_0 + R_1} \\
  &= \SI{3}{\volt} \cdot \frac{\SI{10000}{\ohm}}{R_0 + \SI{10000}{\ohm}} \\
  &= \SI{3}{\volt} \cdot \frac{\SI{10000}{\ohm}}{(\SI{10000}{\ohm} + \SI{60}{\ohm\per\degreeFahrenheit} \cdot T) + \SI{10000}{\ohm}} \\
  &= \SI{3}{\volt} \cdot \frac{\SI{10000}{\ohm}}{(\SI{10000}{\ohm} + \SI{60}{\ohm\per\degreeFahrenheit} \cdot \SI{70}{\degreeFahrenheit}) + \SI{10000}{\ohm}} \\
  &= \SI{3}{\volt} \cdot \frac{\SI{10000}{\ohm}}{(\SI{10000}{\ohm} + \SI{4200}{\ohm}) + \SI{10000}{\ohm}} \\
  &= \SI{3}{\volt} \cdot \frac{\SI{10000}{\ohm}}{\SI{14200}{\ohm} + \SI{10000}{\ohm}} \\
  &= \SI{3}{\volt} \cdot \frac{\SI{10000}{\ohm}}{\SI{24200}{\ohm}} \\
  &= \SIfrac{30000}{24200}{\volt} \\
  &\approx \fbox{\SI{1.24}{\volt}}
\end{align*}

\subsubsection{If $V_0 = \SI{1.339}{\volt}$, what is the room temperature?}
\begin{align*}
  V_0 &= \SI{3}{\volt} \cdot \frac{R_1}{R_0 + R_1} \\
  \SI{1.339}{\volt} &= \SI{3}{\volt} \cdot \frac{\SI{10000}{\ohm}}{(\SI{10000}{\ohm} + \SI{60}{\ohm\per\degreeFahrenheit} \cdot T) + \SI{10000}{\ohm}} \\
  \frac{\num{1.339}}{\num{30000}} &= \frac{\SI{1}{\ohm}}{(\SI{10000}{\ohm} + \SI{60}{\ohm\per\degreeFahrenheit} \cdot T) + \SI{10000}{\ohm}} \\
  \frac{\num{30000}}{\num{1.339}} &= \frac{(\SI{10000}{\ohm} + \SI{60}{\ohm\per\degreeFahrenheit} \cdot T) + \SI{10000}{\ohm}}{\SI{1}{\ohm}} \\
  &= \frac{\SI{20000}{\ohm} + \SI{60}{\ohm\per\degreeFahrenheit} \cdot T}{\SI{1}{\ohm}} \\
  &= \num{20000} + \SI{60}{\per\degreeFahrenheit} \cdot T \\
  \frac{\num{30000}}{\num{1.339}} - \num{20000} &= \SI{60}{\per\degreeFahrenheit} \cdot T \\
  T &=\frac{\frac{\num{30000}}{\num{1.339}} - \num{20000}}{60}\,\si{\degreeFahrenheit} \\
  &\approx \fbox{\SI{40.1}{\degreeFahrenheit}}
\end{align*}

\subsection*{Assume the resistance function of the thermistor $R_0$ is a nonlinear function, and is stored as a table (shown below) in the memory of an embedded system. Each row of the table is the resistance at a specific temperature ($\si{\degreeFahrenheit}$).}
\setcounter{subsubsection}{0}
\subsubsection{How many bytes are needed in minimum for each row to record both the temperature and the resistance?}
It takes $\lceil{\log_{2}{N}}\rceil$ bits to differentiate between $N$ distinct values. To represent an arbitrary element of the range $[m,n]$, then, requires $\lceil{\log_{2}(n-m+1)}\rceil$ bits.

If we choose to represent the temperature as an arbitrary element of the range $[-50,200]$, we will need

\begin{align*}
  \lceil{\log_{2}(n-m+1)}\rceil &= \lceil{\log_{2}(200-(-50)+1)}\rceil \\
  &= \lceil{\log_{2}(251)}\rceil \\
  &= 8 \\
\end{align*}

bits, or one byte for each temperature entry. Similarly, if we choose to represent the resistance as an arbitrary element of the range $[8000,20000]$, we will need

\begin{align*}
  \lceil{\log_{2}(n-m+1)}\rceil &= \lceil{\log_{2}(20000-8000+1)}\rceil \\
  &= \lceil{\log_{2}(12001)}\rceil \\
  &= 14 \\
\end{align*}

bits for each resistance entry. This requires two bytes' storage.

Thus, if we choose a simple biased-integer representation, we need \fbox{three bytes'} total storage per row.

\subsubsection{How many bytes of memory are needed to store the complete table?}
Assuming there is exactly one entry for each temperature value in the range $[-50,200]$ (\si{\degreeFahrenheit}), there are $200-(-50)+1 = 251$ rows. Assuming further that no padding is added to the representation of a row (e.g., to make row entries word-aligned), the table will then occupy $3 \cdot 251 = $ \fbox{$753$ bytes} of memory.

\subsection*{Use an INA2128 chip to produce the signal $y = 5 + 26 \cdot x$, where $x$ is the input and $y$ is the output.}
\setcounter{subsubsection}{0}
\subsubsection{Make a schematic of the circuit, and show the value of the components used in the schematic.}

\subsubsection{Explain your schematic. For example, if you find a figure or a formula in the manual that helps you make the schematic, you should cite the figure or the formula in the explanation of your schematic and explain what help you get from it.}

\subsection*{Follow the guide of Javadoc style at \url{http://en.wikipedia.org/wiki/Javadoc} to document the command {\ttfamily receive} in the interface {\ttfamily Receive}.}
\setcounter{subsubsection}{0}

\lstinputlisting{receive.nc}

\end{document}
